|

### 2021-06-01 supplementary_information_pnas.Rmd
edits: correct paths

  ## read gis files
  filename <- list.files(path = here::here('empirical/data_gis'), full.names = T)
  wsd_subset <- lapply(filename[str_detect(filename, "wsd_subset")], st_read)
  point_subset <- lapply(filename[str_detect(filename, "point_subset")], st_read)
  shape <- lapply(filename[str_detect(filename, "shape")], st_read)
  shape[[1]] <- st_set_crs(shape[[1]], st_crs(wsd_subset[[1]]))

  ## read theory file
  dat_sim <- read_csv(here::here('theory/result/result_sim2020-11-10.csv'))

@@

  # Hokkaido data
  dat_hkd <- read_csv(here::here("empirical/data_out/data_hkd.csv")) %>% mutate(region = "hokkaido")
  dat_hkd_site <- read_csv(here::here('empirical/data_out/data_hkd_site.csv'))

  # Midwest data
  dat_mw <- read_csv(here::here("empirical/data_out/data_mw.csv")) %>% mutate(region = "midwest")
  dat_mw_site <- read_csv(here::here('empirical/data_out/data_mw_site.csv')) %>% 
    mutate(Year = format(as.Date(Date, format = '%m/%d/%Y'), "%Y"))

@@

  ## sensitivity
  source(here::here('theory/table_sensitivity_analysis.R'))

@@

  source(here::here('theory/table_sim_parameter_sensitivity.R'))
  table_output

@@

  source(here::here('theory/table_sim_parameter_main.R'))
  table_output

@@

  source(here::here('empirical/table_splist_hkd.R'))
  table_output

@@

  source(here::here('empirical/table_splist_mw.R'))
  table_output

@@

  source(here::here('empirical/table_apcomp.R'))
  table_output

@@

source(here::here("theory/figure_alpha_pattern.R"))

@@

source(here::here("theory/figure_n_patch_si.R"))

@@

source(here::here("theory/figure_p_branch_si.R"))

@@

source(here::here('empirical/figure_correlation.R'))

@@

source(here::here('empirical/figure_iNEXT_sim.R'))

>>>>

  ## read gis files
  filename <- list.files(path = here::here('code_empirical/data_gis'), full.names = T)
  wsd_subset <- lapply(filename[str_detect(filename, "wsd_subset")], st_read)
  point_subset <- lapply(filename[str_detect(filename, "point_subset")], st_read)
  shape <- lapply(filename[str_detect(filename, "shape")], st_read)
  shape[[1]] <- st_set_crs(shape[[1]], st_crs(wsd_subset[[1]]))

  ## read theory file
  dat_sim <- read_csv(here::here('code_theory/result/result_sim2020-11-10.csv'))

@@

  # Hokkaido data
  dat_hkd <- read_csv(here::here("code_empirical/data_out/data_hkd.csv")) %>% mutate(region = "hokkaido")
  dat_hkd_site <- read_csv(here::here('code_empirical/data_out/data_hkd_site.csv'))

  # Midwest data
  dat_mw <- read_csv(here::here("code_empirical/data_out/data_mw.csv")) %>% mutate(region = "midwest")
  dat_mw_site <- read_csv(here::here('code_empirical/data_out/data_mw_site.csv')) %>% 
    mutate(Year = format(as.Date(Date, format = '%m/%d/%Y'), "%Y"))

@@

  ## sensitivity
  source(here::here('code_theory/table_sensitivity_analysis.R'))

@@

  source(here::here('code_theory/table_sim_parameter_sensitivity.R'))
  table_output

@@

  source(here::here('code_theory/table_sim_parameter_main.R'))
  table_output

@@

  source(here::here('code_empirical/table_splist_hkd.R'))
  table_output

@@

  source(here::here('code_empirical/table_splist_mw.R'))
  table_output

@@

  source(here::here('code_empirical/table_apcomp.R'))
  table_output

@@

source(here::here("code_theory/figure_alpha_pattern.R"))

@@

source(here::here("code_theory/figure_n_patch_si.R"))

@@

source(here::here("code_theory/figure_p_branch_si.R"))

@@

source(here::here('code_empirical/figure_correlation.R'))

@@

source(here::here('code_empirical/figure_iNEXT_sim.R'))
